% Appendix 1: Personal Projects Developed

\ccvattachment{1}{Appendix I}{\textbf{Personal Projects Developed}}

\ccvitem{\textbf{Notification Agenda}\\ Android Application}{\href{http://play.google.com/store/apps/details?id=net.ricardoamaral.apps.notificationagenda}{http://play.google.com/\ldots/details?id=net.ricardoamaral.apps.notificationagenda}}
\ccvitem{Technologies Used}{Android SDK}
\ccvitem{Project Summary}{Simple application which turns small notes into pleasing status bar notifications with fancy high quality icons.}

\fancyfoot{}

\tabularnewline

\ccvitem{\textbf{FireNotes}\\ Windows Application}{}
\ccvitem{Technologies Used}{C\#}
\ccvitem{Project Summary}{A simple tool with a personalized look and feel that allows you to take notes in a conveniently and organized way.}

\tabularnewline

\ccvitem{\textbf{Network Switcher}\\ Windows Application}{}
\ccvitem{Technologies Used}{VB.NET}
\ccvitem{Project Summary}{This application with an intuitive interface allowing you to configure your computer network adapters and switch between configurations through profiles.}

\tabularnewline

\ccvitem{\textbf{Easy Settings}\\ .NET Library}{}
\ccvitem{Technologies Used}{C\# / XML}
\ccvitem{Project Summary}{Simple and easy to use library to manage settings/preferences of any application developed in any .NET language, storing them in an XML file.}

\tabularnewline

\ccvitem{\textbf{Other Projects}}{In addition to the most relevant projects and outlined above, there are others that can be found on my \href{http://github.com/rfgamaral}{GitHub} profile and/or on my personal website; depending on their open source development context, or not.}

% Appendix 2: University Projects Developed

\ccvattachment{2}{Appendix II}{\textbf{University Projects Developed}}

\ccvitem{\textbf{Travel Recommendation System}\\ Windows Application}{Computer Labs IV\newline Orlando Belo}
\ccvitem{Technologies Used}{C\# / UML / SQL Server / ASP.NET / Razor / MVC}
\ccvitem{Project Summary}{This project involved the conception, analysis and requirements specification, development, documentation and maintenance of a software system. The submitted idea to accomplish this project within the proposed  `Travel Recommendation System' was ``low cost flights in Europe''.}

\tabularnewline

\ccvitem{\textbf{UDP.Friendly}\\ Windows Application}{Computer Communications\newline António Costa}
\ccvitem{Technologies Used}{C\# / UDP}
\ccvitem{Project Summary}{The main purpose of this project was to develop a protocol layer over UDP allowing the data transmission rate to be adjusted according to the network load levels. As proof of concept two applications were developed --- according to the client-server model --- enabling transmission of data.}

\tabularnewline

\ccvitem{\textbf{Treasure: Planet XPTO}\\ Windows Game}{Computer Graphics\newline António Ramires Fernandes}
\ccvitem{Technologies Used}{C \& C++ / OpenGL \& GLUT}
\ccvitem{Project Summary}{This projected aimed the development of some sort of Role-Playing Game both in first and third person. The objective was to employ the knowledge acquired throughout the semester, involving concepts such as coordinate systems, lighting, textures, Display Lists, View Frustum Culling, VBOs, etc\ldots}

\tabularnewline

\ccvitem{\textbf{Turtly Turtle Movie Database}\\ Windows and Web Application}{Databases\newline José Manuel Machado}
\ccvitem{Technologies Used}{C\# / PHP / HTML / CSS / JavaScript \& jQuery / Oracle \& PL/SQL}
\ccvitem{Project Summary}{This project aimed to acquire knowledge of the Oracle DBMS, having the film industry as theme. Two applications were developed, one as a Web front end for users to consult information and a Desktop one for database administration and maintenance.}

\tabularnewline

\ccvitem{\textbf{Simplex Algorithm}\\ Web Application}{Deterministic Models of Operational Research\newline José António Oliveira}
\ccvitem{Technologies Used}{PHP / HTML / CSS / JavaScript \& jQuery}
\ccvitem{Project Summary}{This project consisted in developing an application capable of solving maximization and minimization linear programming problems. These problems were solved resorting to an implementation of the Simplex algorithm, with Primal or Dual feasibility.}

\tabularnewline

\ccvitem{\textbf{Just Friends / Always Connected}\\ Linux and Windows Application}{Computer Labs III\newline António Nestor Ribeiro \& Luís Paulo Santos}
\ccvitem{Technologies Used}{C / Java / Swing / MVC}
\ccvitem{Project Summary}{Bound to the same Curricular Unit, two quite similar projects were developed. Both consisted in the development or use of data structures --- using different languages --- being both implementations based in a simplified version of the LinkedIn social network.}

\tabularnewline

\ccvitem{\textbf{AEROGEST}\\ Windows Application}{Object-Oriented Programming\newline F. Mário Martins}
\ccvitem{Technologies Used}{Java}
\ccvitem{Project Summary}{This project aimed to apply all the knowledge acquired throughout the semester about the object-oriented programming paradigm. The project consisted in developing a ``flight management system''.}

\tabularnewline

\ccvitem{\textbf{Remark}}{The projects above do not account for all projects developed during the undergraduate school, being listed only those deemed most important or relevant.}